\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-03-02 manuscript/paper.tex
Update the graph representation of joint model

\subsection{Graphical model}
Figure~\ref{fig:graphical-model} below gives the graphical representation for the lights model to get a beter view of the dependence structure for the model.
\begin{figure}[!htb]
\centering
\resizebox{.9\textwidth}{!}{
\begin{tikzpicture}
\hspace{3cm}
\tikzstyle{main}=[circle, minimum size = 18mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{var}=[rectangle, minimum size = 16mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[var, fill = white!100] (beta) [] {\Large$\bm{\beta_k^l}$};
  \node[var, fill = white!100] (xi) [below=4cm of beta] {\Large$\bm{\xi_k}$};
  \node[var, fill = white!100] (gamma) [below=3cm of xi] {\Large$\bm{\gamma_k}$};
  \node[main, fill = white!100] (G) [right=4cm of xi] {\Large$\bm{G_i}$};
  \node[main, fill = white!100] (mu) [right=4cm of beta] {\Large$\bm{M_{ik}^l(t)}$};
  \node[main, fill = black!30] (Y) [right=of mu] {\Large$\bm{Y_i^l(t)}$};
  \node[main, fill = white!100] (b) [above=of mu] {\Large$\bm{b_i^l}$};
  \node[var, fill = white!100] (phi) [above=of Y] {\Large$\bm{\phi_l}$};
  \node[var, fill = white!100] (Sigma) [left=of b] {\Large$\bm{D}$};
  \node[main, fill = white!100] (W) [below=3cm of Y] {\Large$\bm{\Psi_i(t)}$};
  \node[main, fill = white!100] (lambda) [right=4cm of gamma] {\Large$\bm{\lambda_i(t)}$};
  \node[main, fill = black!30] (T) [right=of lambda] {\Large$\bm{T_i}$};
  \node[main, fill = black!30] (X) at (3, -8.3) {\Large$\bm{X_i}$};

  \path [->,draw,ultra thick]
        (beta) edge (mu)
        (G) edge (mu)
        (b) edge (mu)
        (mu) edge (Y)
        (Sigma) edge (b)
        (phi) edge (Y)
        (xi) edge (G)
        (X) edge (G)
        (gamma) edge (lambda)
        (W) edge (lambda)
        (G) edge (lambda)
        (lambda) edge (T)
        (Y) edge (W)
        ;

  \node[rectangle, inner sep=8mm,draw=black!100, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.5cm, xshift=-10mm]{\Large$\bm{k = 1...K}$}}] at (0, -4.6) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick] at (8, 4.1) {\Large$\bm{l = 1...L}$};

  \node[rectangle,inner sep=6mm, draw=black!100, label=center:\rotatebox{90}{\color{white}\Large{\textbf{Longitudinal}}}, minimum width=1cm, minimum height = 6cm, fill = black!50] at (-2.7,0.5) {};

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:\rotatebox{90}{\color{white}\Large{\textbf{Time-to-event}}}, minimum width=1cm, minimum height = 6cm, fill = black!50] at (-2.7,-8.2) {};

>>>>

\subsection{Graphical model}
Figure~\ref{fig:graphical-model} below gives the graphical representation for the lights model to get a beter view of the dependence structure for the model.
\begin{figure}[!htb]
\centering
\resizebox{.9\textwidth}{!}{
\begin{tikzpicture}
\tikzstyle{main}=[circle, minimum size = 18mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{var}=[rectangle, minimum size = 16mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[var, fill = white!100] (beta) [] {\Large$\bm{\beta_k^l}$};
  \node[main, fill = white!100] (mu) [below=4cm of beta] {$\bm{M_{ik}^l(t)}$};
  \node[main, fill = black!30] (Y) [below=of mu] {\Large$\bm{Y_i^l(t)}$};
  \node[main, fill = white!100] (b) [left=of mu] {\Large$\bm{b_i^l}$};
  \node[var, fill = white!100] (phi) [left=of Y] {\Large$\bm{\phi_l}$};
  \node[var, fill = white!100] (Sigma) [above=of b] {\Large$\bm{D}$};
  \node[var, fill = white!100] (xi) [right=4.5cm of beta] {\Large$\bm{\xi_k}$};
  \node[var, fill = white!100] (gamma) [right=5cm of xi] {\Large$\bm{\gamma_k}$};
  \node[main, fill = white!100] (G) [below=4cm of xi] {\Large$\bm{G_i}$};
  \node[main, fill = white!100] (W) [right=8.5cm of Y] {\Large$\bm{\Psi_i(t)}$};
  \node[main, fill = white!100] (lambda) [below=4cm of gamma] {\Large$\bm{\lambda_i(t)}$};
  \node[main, fill = black!30] (T) [below=1.3cm of lambda] {\Large$\bm{T_i}$};
  \node[main, fill = black!30] (X) at (4, -3.3) {\Large$\bm{X_i}$};

  \path [->,draw,ultra thick, blue]
        (G) edge (mu)
        (Y) edge (W);
  \path [->,draw,ultra thick]
        (beta) edge (mu)
        (b) edge (mu)
        (mu) edge (Y)
        (Sigma) edge (b)
        (phi) edge (Y)
        (xi) edge (G)
        (X) edge (G)
        (gamma) edge (lambda)
        (W) edge (lambda)
        (G) edge (lambda)
        (lambda) edge (T)
        ;

  \node[rectangle, inner sep=8mm,draw=black!130, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.4cm, xshift=-8cm]{\Large$\bm{k = 1...K}$}}] at (6.5,0.4) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick, label={[anchor=west, yshift=-0.5cm, xshift=-2.7cm]{\Large$\bm{l = 1...L}$}}] {};

  \node[rectangle,inner sep=6mm, draw=black!100, label=center:{\color{white}\Large{\textbf{Longitudinal}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (-1.5,2.8) {};

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:{\color{white}\Large{\textbf{Time-independent}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (5,2.8) {};

  \node[rectangle,inner sep=6mm, draw=black!100,  label=center:{\color{white}\Large{\textbf{Time-to-event}}}, minimum width=5cm, minimum height = 1cm, fill = black!50] at (11.5,2.8) {};
